Towards Verifying the Bitcoin-S Library

### 2019-06-22 paper/paper.tex
add final stainless output
fix indentation

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] number/NumberType.scala:8:30: Unknown type parameter type T
  sealed abstract class Number[T <: Number[T]] {
                               ^^^^^^^^^^^^^^

\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] number/NumberType.scala:9:3: Could not extract tree in class: type A = BigInt (class scala.reflect.internal.Trees$TypeDef)
               type A = BigInt
               ^^^^^^^^^^^^^^^

\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] number/NumberType.scala:33:14: Unknown call to & on result (BigInt) with arguments List(Number.this.andMask) of type List(BigInt)
               require((result & andMask) == result,
                       ^^^^^^^^^^^^^^^^

\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] number/NumberType.scala:9:3: Could not extract tree in class: type A = BigInt (class scala.reflect.internal.Trees$TypeDef)
            type A = BigInt
            ^^^^^^^^^^^^^^^
  [Warning ] number/NumberType.scala:71:3: Could not extract tree in class: scala.this.Predef.require(Int64Impl.this.underlying.>=(math.this.BigInt.long2bigInt(-9223372036854775808L)), "Number was too small for a int64, got: ".+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
            require(underlying >= -9223372036854775808L,
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [Warning ] number/NumberType.scala:73:3: Could not extract tree in class: scala.this.Predef.require(Int64Impl.this.underlying.<=(math.this.BigInt.long2bigInt(9223372036854775807L)), "Number was too big for a int64, got: ".+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
            require(underlying <= 9223372036854775807L,
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [ Error  ] checkResult$0 depends on missing dependencies: require$1.

\end{lstlisting}

@@

Stainless output now: \todo{kai special chars again}
% \begin{lstlisting}[style=stainless][Warning ] The Z3 native interface is not available. Falling back onto smt-z3.
%   [  Info  ]  - Checking cache: 'postcondition' VC for + @12:3...
%   [  Info  ]  - Checking cache: 'adt invariant' VC for apply @34:39...
%   [  Info  ]  - Checking cache: 'adt invariant' VC for apply @62:38...
%   [  Info  ] Cache miss: 'adt invariant' VC for apply @62:38...
%   [  Info  ] Cache hit: 'adt invariant' VC for apply @34:39...
%   [  Info  ] Cache hit: 'postcondition' VC for + @12:3...
%   [  Info  ]  - Now solving 'adt invariant' VC for apply @62:38...
%   [  Info  ]  - Result for 'adt invariant' VC for apply @62:38:
%   [Warning ]  => INVALID
%   [Warning ] Found counter-example:
%   [Warning ]   bigInt: BigInt -> -9223372036854775809
%   [  Info  ]  - Checking cache: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
%   [  Info  ] Cache miss: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
%   [  Info  ]  - Now solving 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
%   [  Info  ]  - Result for 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36:
%   [Warning ]  => INVALID
%   [Warning ] Found counter-example:
%   [Warning ]   num: Number   -> Int64Impl(9223372036854775807)
%   [Warning ]   thiss: Number -> Int64Impl(1)
%   [  Info  ]   ┌───────────────────┐
%   [  Info  ] ╔═╡ stainless summary ╞══════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╗
%   [  Info  ] ║ └───────────────────┘                                                                                                                      ║
%   [  Info  ] ║ +      postcondition                                                 valid from cache            currency/CurrencyUnits.scala:12:3   1.266 ║
%   [  Info  ] ║ +      precond. (call checkResult(thiss, underlying(thiss) + u ...)  invalid           U:smt-z3  number/NumberType.scala:17:36       0.089 ║
%   [  Info  ] ║ apply  adt invariant                                                 valid from cache            currency/CurrencyUnits.scala:34:39  0.194 ║
%   [  Info  ] ║ apply  adt invariant                                                 invalid           U:smt-z3  number/NumberType.scala:62:38       0.348 ║
%   [  Info  ] ╟┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄╢
%   [  Info  ] ║ total: 4    valid: 2    (2 from cache) invalid: 2    unknown: 0    time:   1.897                                                           ║
%   [  Info  ] ╚════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╝
%   [  Info  ] Shutting down executor service.
% \end{lstlisting}

@@

Finally, everything is green and correctly verified.
\begin{figure}
	\centering
		\includegraphics[width=\textwidth]{final_verify_output}
	\caption{Output of Stainless verification for addition with 0 of Bitcoin-S-Cores CurrencyUnit}
\end{figure}

The verified code.
\lstinputlisting[style=scala]{../code/currsniporig/src/main/scala/code/end/Code.scala}

>>>>

Stainless output:
\begin{lstlisting}[style=stainless]
[ Error  ] number/NumberType.scala:8:30: Unknown type parameter type T
          sealed abstract class Number[T <: Number[T]] {
                                        ^^^^^^^^^^^^^^
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
[Warning ] number/NumberType.scala:9:3: Could not extract tree in class: type A = BigInt (class scala.reflect.internal.Trees$TypeDef)
              type A = BigInt
              ^^^^^^^^^^^^^^^
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
[ Error  ] number/NumberType.scala:33:14: Unknown call to & on result (BigInt) with arguments List(Number.this.andMask) of type List(BigInt)
              require((result & andMask) == result,
                      ^^^^^^^^^^^^^^^^
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
[Warning ] number/NumberType.scala:9:3: Could not extract tree in class: type A = BigInt (class scala.reflect.internal.Trees$TypeDef)
          type A = BigInt
          ^^^^^^^^^^^^^^^
[Warning ] number/NumberType.scala:71:3: Could not extract tree in class: scala.this.Predef.require(Int64Impl.this.underlying.>=(math.this.BigInt.long2bigInt(-9223372036854775808L)), "Number was too small for a int64, got: ".+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
          require(underlying >= -9223372036854775808L,
          ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
[Warning ] number/NumberType.scala:73:3: Could not extract tree in class: scala.this.Predef.require(Int64Impl.this.underlying.<=(math.this.BigInt.long2bigInt(9223372036854775807L)), "Number was too big for a int64, got: ".+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
          require(underlying <= 9223372036854775807L,
          ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
[ Error  ] checkResult$0 depends on missing dependencies: require$1.
\end{lstlisting}

@@

Stainless output now: \todo{kai special chars again}
% \begin{lstlisting}[style=stainless]
% [Warning ] The Z3 native interface is not available. Falling back onto smt-z3.
% [  Info  ]  - Checking cache: 'postcondition' VC for + @12:3...
% [  Info  ]  - Checking cache: 'adt invariant' VC for apply @34:39...
% [  Info  ]  - Checking cache: 'adt invariant' VC for apply @62:38...
% [  Info  ] Cache miss: 'adt invariant' VC for apply @62:38...
% [  Info  ] Cache hit: 'adt invariant' VC for apply @34:39...
% [  Info  ] Cache hit: 'postcondition' VC for + @12:3...
% [  Info  ]  - Now solving 'adt invariant' VC for apply @62:38...
% [  Info  ]  - Result for 'adt invariant' VC for apply @62:38:
% [Warning ]  => INVALID
% [Warning ] Found counter-example:
% [Warning ]   bigInt: BigInt -> -9223372036854775809
% [  Info  ]  - Checking cache: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
% [  Info  ] Cache miss: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
% [  Info  ]  - Now solving 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
% [  Info  ]  - Result for 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36:
% [Warning ]  => INVALID
% [Warning ] Found counter-example:
% [Warning ]   num: Number   -> Int64Impl(9223372036854775807)
% [Warning ]   thiss: Number -> Int64Impl(1)
% [  Info  ]   ┌───────────────────┐
% [  Info  ] ╔═╡ stainless summary ╞══════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╗
% [  Info  ] ║ └───────────────────┘                                                                                                                      ║
% [  Info  ] ║ +      postcondition                                                 valid from cache            currency/CurrencyUnits.scala:12:3   1.266 ║
% [  Info  ] ║ +      precond. (call checkResult(thiss, underlying(thiss) + u ...)  invalid           U:smt-z3  number/NumberType.scala:17:36       0.089 ║
% [  Info  ] ║ apply  adt invariant                                                 valid from cache            currency/CurrencyUnits.scala:34:39  0.194 ║
% [  Info  ] ║ apply  adt invariant                                                 invalid           U:smt-z3  number/NumberType.scala:62:38       0.348 ║
% [  Info  ] ╟┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄╢
% [  Info  ] ║ total: 4    valid: 2    (2 from cache) invalid: 2    unknown: 0    time:   1.897                                                           ║
% [  Info  ] ╚════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╝
% [  Info  ] Shutting down executor service.
% \end{lstlisting}

@@

Finally, everything is green and correctly verified. \todo{kai special chars}
% \begin{lstlisting}[style=scala]
% [Warning ] The Z3 native interface is not available. Falling back onto smt-z3.
% [  Info  ]  - Checking cache: 'precond. (call apply(Int64(), 1))' VC for one @69:18...
% [  Info  ] Cache hit: 'precond. (call apply(Int64(), 1))' VC for one @69:18...
% [  Info  ]  - Checking cache: 'precond. (call apply(Int64(), bigInt))' VC for apply @52:5...
% [  Info  ] Cache miss: 'precond. (call apply(Int64(), bigInt))' VC for apply @52:5...
% [  Info  ]  - Now solving 'precond. (call apply(Int64(), bigInt))' VC for apply @52:5...
% [  Info  ]  - Result for 'precond. (call apply(Int64(), bigInt))' VC for apply @52:5:
% [  Info  ]  => VALID
% [  Info  ]  - Checking cache: 'precond. (call +(underlying(satoshis(thiss)), underlyin ...)' VC for + @14:14...
% [  Info  ]  - Checking cache: 'postcondition' VC for + @12:3...
% [  Info  ] Cache hit: 'precond. (call +(underlying(satoshis(thiss)), underlyin ...)' VC for + @14:14...
% [  Info  ] Cache miss: 'postcondition' VC for + @12:3...
% [  Info  ]  - Now solving 'postcondition' VC for + @12:3...
% [  Info  ]  - Result for 'postcondition' VC for + @12:3:
% [  Info  ]  => VALID
% [  Info  ]  - Checking cache: 'precond. (call apply(Int64(), -9223372036854775808))' VC for min @71:18...
% [  Info  ] Cache hit: 'precond. (call apply(Int64(), -9223372036854775808))' VC for min @71:18...
% [  Info  ]  - Checking cache: 'adt invariant' VC for apply @34:39...
% [  Info  ] Cache hit: 'adt invariant' VC for apply @34:39...
% [  Info  ]  - Checking cache: 'precond. (call apply(Int64(), 9223372036854775807))' VC for max @72:18...
% [  Info  ] Cache hit: 'precond. (call apply(Int64(), 9223372036854775807))' VC for max @72:18...
% [  Info  ]  - Checking cache: 'adt invariant' VC for apply @79:5...
% [  Info  ] Cache hit: 'adt invariant' VC for apply @79:5...
% [  Info  ]  - Checking cache: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @22:11...
% [  Info  ] Cache hit: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @22:11...
% [  Info  ]  - Checking cache: 'precond. (call apply(Int64(), 0))' VC for zero @68:19...
% [  Info  ] Cache hit: 'precond. (call apply(Int64(), 0))' VC for zero @68:19...
% [  Info  ]   ┌───────────────────┐
% [  Info  ] ╔═╡ stainless summary ╞══════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╗
% [  Info  ] ║ └───────────────────┘                                                                                                                      ║
% [  Info  ] ║ +      postcondition                                                 valid             U:smt-z3  currency/CurrencyUnits.scala:12:3   0.643 ║
% [  Info  ] ║ +      precond. (call +(underlying(satoshis(thiss)), underlyin ...)  valid from cache            currency/CurrencyUnits.scala:14:14  0.097 ║
% [  Info  ] ║ +      precond. (call checkResult(thiss, underlying(thiss) + u ...)  valid from cache            number/NumberType.scala:22:11       0.015 ║
% [  Info  ] ║ apply  adt invariant                                                 valid from cache            currency/CurrencyUnits.scala:34:39  0.005 ║
% [  Info  ] ║ apply  precond. (call apply(Int64(), bigInt))                        valid             U:smt-z3  number/NumberType.scala:52:5        0.187 ║
% [  Info  ] ║ apply  adt invariant                                                 valid from cache            number/NumberType.scala:79:5        0.017 ║
% [  Info  ] ║ max    precond. (call apply(Int64(), 9223372036854775807))           valid from cache            number/NumberType.scala:72:18       0.001 ║
% [  Info  ] ║ min    precond. (call apply(Int64(), -9223372036854775808))          valid from cache            number/NumberType.scala:71:18       0.001 ║
% [  Info  ] ║ one    precond. (call apply(Int64(), 1))                             valid from cache            number/NumberType.scala:69:18       0.915 ║
% [  Info  ] ║ zero   precond. (call apply(Int64(), 0))                             valid from cache            number/NumberType.scala:68:19       0.001 ║
% [  Info  ] ╟┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄╢
% [  Info  ] ║ total: 10   valid: 10   (8 from cache) invalid: 0    unknown: 0    time:   1.882                                                           ║
% [  Info  ] ╚════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╝
% [  Info  ] Shutting down executor service.
% \end{lstlisting}

% \begin{figure}
% 	\centering
% 		\includegraphics[width=\textwidth]{final_verify_output}
% 	\caption{Output of Stainless verification for addition with 0 of Bitcoin-S-Cores CurrencyUnit}
% \end{figure}

The verified code.
\lstinputlisting[style=scala]{../code/addition/src/main/scala/addition/modified/number/NumberType.scala}
\lstinputlisting[style=scala]{../code/addition/src/main/scala/addition/modified/currency/CurrencyUnits.scala}
